Cluster Difference Imaging Photometric Survey. IV. TOI 1937Ab. Young Hot Jupiter, or Just Tidally Spun Up?

### 2021-02-09 planet_paper/ms.tex
minor
paper updates
update paper
planet paper: minor notes

\title{
  Cluster Difference Imaging Photometric Survey. III.
  Subtitle.
}

@@

@@

@@

@@

The future:
- Detailed multi-abundance modelling.
  i.e,. Get spectra of other cluster stars using PFS, and compare the metallicities.
- 2$\farc$5 separate, multiband imager. (With LCOGT, 2m in Australia,
  z-band)->Do PSF fitting.
- K-band image. MagAO? Multicolor imager.
- Maybe GROND -- has K-band. At La Silla. On 2.2m.  griz+K.

>>>>

\title{
  Cluster Difference Imaging Photometric Survey. IV.
  TOI 1937Ab. Young Hot Jupiter, or Just Tidally Spun Up?
}

@@

  \subsection{NGC 2516 broadly}
  \subsection{TOI 1937 specifically}
  If you back-integrate 20 Myr, it gets closer. But then, it gets
  further.

@@

\pararaph{Metallicity}
(Quoting Jilinski+09)
``After an initial period where several authors (see Terndrup et al.
2002) found for NGC 2516 a metallicity of a few tenths dex below the
solar, more recent analysis (Irwin et al. 2007; Jeffries et al.  2001;
Sciortino et al. 2001; Sung et al. 2002) places NGC 2516 with a
metallicity close to solar. ''

@@

\paragraph{Mass} 1.8Mjup

\paragraph{Obliquity} Less than 20 deg or so. Consistent with
expectations given its short orbital period (e.g., Anderson et al
2021).

@@

\subsection{The present}

The minimum orbital period beyond which a planet is tidally sheared
apart depends on the concentration of mass within the planet
(Rappaport+2013).
For a VERY CENTRALLY CONCENTRATED planet with \tn's
mean density of 0.XX g/cm3, this period is XX.X hours.
For the limit of a uniform density distribution, the period would be
XX.X hours.

is

XX.X hr (e.g., Rappaport+ 2013).
Given ,

The Roche limit

Roche limit for a close-orbiting planet can
be expressed as a minimum orbital period depending
on the density distribution of the planet (Rappaport
et al. 2013). For WASP-12b, with a mean density of
0.46 g cm􀀀3, the Roche-limiting orbital period is 14.2 hr
assuming the mass of the planet to be concentrated near
the center, and 18.6 hr in the opposite limit of a spher-
ical and incompressible planet. The

\subsection{The future}:
- Detailed multi-abundance modelling.
  i.e,. Get spectra of other cluster stars using PFS, and compare the metallicities.
- 2$\farc$5 separate, multiband imager. (With LCOGT, 2m in Australia,
  z-band)->Do PSF fitting.
- K-band image. MagAO? Multicolor imager.
- Maybe GROND -- has K-band. At La Silla. On 2.2m.  griz+K.
